Notes on Wide Gap

### 2016-03-25 paper/wide_gap_notes.tex
added beta factor
wait, base velocity state should be different in wide gap

Note: two things are currently missing. The constant $\beta$ from the nondimensionalization, and the Coriolis term in the momentum equation.

@@

\beq
\mathbf{B} = B_0 \hat{z} + \mathbf{B_1}
\eeq

@@

@@

\begin{multline}
\frac{1}{r}\partial_t \left(\nabla^2 \Psi - \frac{2}{r} \partial_r \Psi \right) + J\left(\Psi, \frac{1}{r^2} \left( \nabla^2 \Psi - \frac{2}{r} \partial_r\Psi\right) \right) - \frac{1}{r} 2 u_\phi \partial_z u_\phi \\
= J\left(A, \frac{1}{r^2} \left( \nabla^2 A - \frac{2}{r} \partial_rA\right) \right) - \frac{2}{r}B_\phi \partial_z B_\phi \\
+ \frac{1}{\reye} \left[ \nabla^2 \left(\frac{1}{r} \nabla^2 \Psi\right) - \frac{1}{r^3} \partial_r^2 \Psi - \frac{1}{r^4}\partial_r\Psi\right] + \frac{1}{r}B_0 \partial_z \left(\nabla^2 A - \frac{2}{r} \partial_r A\right)
\end{multline}

@@

\begin{equation}
  \label{eq:uy_perturbed}
\partial_t \uphi + \frac{J(\psi, \uphi)}{r} + \frac{\uphi \partial_z \psi}{r^2} - \frac{2}{r}q \Omega_0 \partial_z \Psi= \frac{J(A, B_\phi)}{r} + \frac{B_\phi \partial_z A}{r^2} + \frac{1}{\reye} \left( \nabla^2 \uphi - \frac{\uphi}{r}\right) + B_0 \partial_z B_\phi
\end{equation}

>>>>

Note: currently missing the Coriolis term in the momentum equation. %The Coriolis and centrifugal terms add a $-2\partial_z u_\phi$ term to the LHS of the $\Psi$ equation and a $+2$

@@

\beq
\mathbf{B} = B_0 \hat{z} + \mathbf{B_1},
\eeq

which is the same perturbation we used in the thin-gap construction. But wait! We perturbed the thin-gap equations according to

@@

but I don't think this is valid in the wide-gap case. To be sure, I'm going to perturb instead by

\beq
\mathbf{u} = r\Omega(r)\hat{\phi}+ \mathbf{u_1}
\eeq

where $\Omega(r) = \Omega_0 \left(\frac{r}{r_0}\right)^{-q} = \Omega_0 \left(r\right)^{-q}$ in dimensionless coordinates (but keeping $\Omega_0$ to flag a rotational term...) Agreed?

@@

\begin{multline}
\frac{1}{r}\partial_t \left(\nabla^2 \Psi - \frac{2}{r} \partial_r \Psi \right) + J\left(\Psi, \frac{1}{r^2} \left( \nabla^2 \Psi - \frac{2}{r} \partial_r\Psi\right) \right) - \frac{1}{r} 2 u_\phi \partial_z u_\phi \\
= \frac{2}{\beta} J\left(A, \frac{1}{r^2} \left( \nabla^2 A - \frac{2}{r} \partial_rA\right) \right) - \frac{2}{\beta} \frac{2}{r}B_\phi \partial_z B_\phi \\
+ \frac{1}{\reye} \left[ \nabla^2 \left(\frac{1}{r} \nabla^2 \Psi\right) - \frac{1}{r^3} \partial_r^2 \Psi - \frac{1}{r^4}\partial_r\Psi\right] + \frac{2}{\beta} \frac{1}{r}B_0 \partial_z \left(\nabla^2 A - \frac{2}{r} \partial_r A\right)
\end{multline}

@@

\begin{equation}
  \label{eq:uy_perturbed}
\partial_t \uphi + \frac{J(\psi, \uphi)}{r} + \frac{\uphi \partial_z \psi}{r^2} - \frac{2}{r}q \Omega_0 \partial_z \Psi= \frac{2}{\beta} \frac{J(A, B_\phi)}{r} + \frac{2}{\beta} \frac{B_\phi \partial_z A}{r^2} + \frac{1}{\reye} \left( \nabla^2 \uphi - \frac{\uphi}{r}\right) + \frac{2}{\beta} B_0 \partial_z B_\phi
\end{equation}
